---
title: "W6 D2 Homework"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
```

```{r}
reviews <- read_csv("data/20190928-items.csv") %>% 
  clean_names()
```

## Question 2.
>Find the brand with the highest numbers of phones in the dataset.

```{r}
reviews %>% 
  ggplot(aes(x = brand)) +
  geom_bar()

reviews %>% 
  group_by(brand) %>% 
  summarise(total_phones = n())
```

Samsung has the most phones

## Question 3.
>For your top brand, plot the distribution of phone ratings as a probability density, overlaying a fitted normal distribution. Do you think the normal distribution provides a good model of these ratings?

```{r}
samsung_reviews <- reviews %>% 
  filter(brand == "Samsung")

samsung_unique_reviews <- reviews %>% 
  filter(brand == "Samsung") %>% 
  group_by(rating) %>% 
  summarise(count = n()) %>% 
  mutate(prob = count / nrow(samsung_reviews))

samsung_stats <- samsung_reviews %>% 
  summarise(
    num = n(),
    mean = mean(rating),
    sd = sd(rating)
  )

samsung_reviews %>% 
  ggplot(aes(x = rating)) +
  geom_histogram(aes(y = after_stat(density)),
                 col = "white",
                 bins = nrow(samsung_unique_reviews)) +
  scale_x_continuous(breaks = seq(0, 5, 0.5)) +
  stat_function(fun = dnorm,
                args = list(
                  mean = samsung_stats$mean,
                  sd = samsung_stats$sd
                ),
                col = "red")
```

No, a normal distribution isn't a good model for these ratings. The density doesn't decrease uniformly from the mean.

## Question 4 
>We can be more quantitative in comparing the distribution of top brand ratings with a normal distribution. You calculated the mean() and sd() of your distribution in an earlier question. Use these values to calculate the proportions of ratings within one-, two- and three standard deviations of the mean. Compare these proportions with those you expect for a normal distribution.

```{r}
samsung_scaled <- reviews %>% 
  filter(brand == "Samsung") %>% 
  mutate(z_rating = scale(rating)) %>% 
  group_by(rating) %>% 
  summarise(count = n(), z_rating) %>% 
  mutate(prob = count / nrow(samsung_reviews)) %>% 
  distinct()

samsung_1_sd <- samsung_scaled %>% 
  filter(between(z_rating, left = -1, right = 1))

samsung_2_sd <- samsung_scaled %>% 
  filter(between(z_rating, left = -2, right = 2))

samsung_3_sd <- samsung_scaled %>% 
  filter(between(z_rating, left = -3, right = 3))

prop_sd1 <- 100 * (nrow(samsung_1_sd) / nrow(samsung_scaled))
prop_sd2 <- 100 * (nrow(samsung_2_sd) / nrow(samsung_scaled))
prop_sd3 <- 100 * (nrow(samsung_3_sd) / nrow(samsung_scaled))

normal_sd <- c(100 * (pnorm(q = 1) - pnorm(q = -1)),
               100 * (pnorm(q = 2) - pnorm(q = -2)),
               100 * (pnorm(q = 3) - pnorm(q = -3)))

tibble(
  samsung = round(c(prop_sd1,prop_sd2,prop_sd3),2),
  normal = round(normal_sd, 2)
)
```

```{r}
qqnorm(samsung_reviews$rating)
qqline(samsung_reviews$rating, col = "red")
```

Comparing our data to a normal distribution, if our distribution was a straight line (followed the red line), then it would be a normal distribution. Because it doesn't, it isn't.


