---
title: "Simple linear regression homework"
output: html_notebook
---

```{r libraries}
library(tidyverse)
library(modelr)
library(ggfortify)
```

```{r data}
project <- read_csv("data/project_management.csv")
```
# MVP

```{r}
project %>% 
    ggplot(aes(x = estimated_length, y = actual_length)) +
    geom_point()
```


Correlation coefficient:

```{r}
cor(project$estimated_length, project$actual_length)
```

0.8 means strong positive correlation between estimated length and actual length


```{r}
model <- lm(formula = actual_length ~ estimated_length,
   data = project)

summary(model)
```
R squared suggests that 64.75% of the estimated job length can be explained by the actual job length.

The p-value (1.91e-12) strongly suggests the contribution is statistically significant.

```{r}
autoplot(model)
```

Residuals vs Fitted broadly suggests that the residuals are independent, and the quantile-quantile plot implies a normal distribution. On top of this, Scale-Location suggests that the variation of the residuals is reasonably constant.

All three plots together support the p-value as being reliable, meaning that the estimated job time is in fact broadly based in reality.