---
title: "GGPlot Homework"
output: html_notebook
---

```{r libraries}
library(tidyverse)
library(CodeClanData)
```

```{r data import}
qb_revenue_breakdown <- qb_revenue_breakdown
qb_monthly_sales <- qb_monthly_sales
qb_competitors <- qb_competitors
qb_device_data <- qb_device_data
```

# Part 1
### Question 1

Take the data in the dataset qb_revenue_breakdown and make a stacked bar chart showing the sources of revenue across the two years in the dataset.

```{r}
qb_revenue_breakdown %>% 
  janitor::clean_names() %>% 
  ggplot(aes(product, revenue, fill = year)) +
  geom_bar(stat = "identity") +
  labs(x = "\nProduct",
       y = "Revenue\n",
       fill = "Year",
       title = "Revenue Sources 2018/19")
```

### Question 2

Make a line chart showing monthly sales of the “flagship product” - the ‘KwikBit Unit 1’ - over the last year. This data is inside `qb_monthly_sales`, but you will need to use filter() or subset() (base R).

```{r}
qb_monthly_sales %>%
  janitor::clean_names() %>% 
  filter(cashflow == "Kwikbit Unit 1 Sales") %>%
  ggplot(aes(date, amount)) +
  geom_line() +
  labs(x = "\nDate",
       y = "Revenue\n",
       title = "Monthly Kwikbit Unit 1 Sales") +
  theme_light()
```

### Question 3

Make a line chart showing monthly revenue and costs over the last year. This data is also in qb_monthly_sales.

```{r}
qb_monthly_sales %>%
  janitor::clean_names() %>% 
  filter(cashflow != "Kwikbit Unit 1 Sales",
         date > "2018-12-31") %>% 
  ggplot(aes(x = date, y = amount, colour = cashflow)) +
  geom_line() +
  labs(x = "\nMonth",
       y = "Amount\n",
       colour = "",
       title = "Monthly Incoming and Outgoings") +
  theme_light()
```

### Question 4

Show annual sales of personal fitness trackers over the last 5 years broken down by company as a ribbon plot (use geom_area). This data is in qb_competitors.

```{r}
comp_max_min <- qb_competitors %>%
  janitor::clean_names() %>% 
  group_by(year) %>% 
  summarise(min = min(revenue), max = max(revenue))

comp_combined <- qb_competitors %>% 
  janitor::clean_names() %>% 
  inner_join(comp_max_min, by = "year")

comp_combined %>% 
  ggplot(aes(year)) +
  geom_ribbon(aes(ymin = min, ymax = max)) +
  geom_line(size = 1.3, aes(y = revenue, colour = company)) +
  ggthemes::theme_stata()
```

### Question 5

Now show the sales from the four competitors as a line graph. Include an extra layer that shows the data points used to make the lines.

```{r}
qb_competitors %>% 
  janitor::clean_names() %>% 
  ggplot(aes(year, revenue, colour = company)) +
  geom_line() +
  geom_point() +
  ggthemes::theme_stata()
```

### Question 6

Now the company wants to compare the number of steps that their device counts vs. their competitors. Make a line graph of the number of steps throughout time, and use faceting to compare between companies and people. The data for this is in qb_device_data.

```{r}
qb_device_data %>% 
  janitor::clean_names() %>% 
  mutate(time = (hours*60) + mins) %>% 
  ggplot(aes(time, counts, colour = device)) +
  geom_line() +
  facet_grid(device ~ id) +
  labs(y = "Steps",
      x = "Time (mins)",
      colour = "Device") +
  ggthemes::theme_stata() +
  theme(axis.text.y = element_text(angle = 0, size = 9),
        strip.text = element_text(size = 10))
```


