---
title: "Week 6 Day 1 Homework"
output: html_notebook
---

```{r}
library(gtools)
library(tidyverse)
source("prob.R")
boat <- read_csv("data/titanic.csv")
```
```{r}
boat <- boat %>% 
  mutate(type = case_when(
    class %in% c("3rd", "2nd", "1st") ~ "Passenger",
    TRUE ~ "Crew"
  ))

boat_crew <- boat %>% 
  filter(type == "Crew")

boat_passengers <- boat %>% 
  filter(type == "Passenger")
```

# Titanic

```{r}
boat %>% 
  filter(survived == "yes") %>% 
  summarise(prob_all = n() / nrow(boat))

boat_crew %>% 
  filter(survived == "yes") %>% 
  summarise(prob_crew = n() / nrow(boat_crew))

boat_passengers %>% 
  filter(survived == "yes") %>% 
  summarise(prob_passengers = n() / nrow(boat_passengers))
```

23.7% of crew survived, 37.965% of passengers survived. Seems fairly definitive to me!

### Ignore this. I wanted to mess around with exploring across populations!

```{r}
boat_passengers_women <- boat_passengers %>% 
  filter(gender == "female")

boat_passengers_men <- boat_passengers %>% 
  filter(gender == "male")

boat_passengers_1st <- boat_passengers %>% 
  filter(class == "1st")

boat_passengers_2nd <- boat_passengers %>% 
  filter(class == "2nd")

boat_passengers_3rd <- boat_passengers %>% 
  filter(class == "3rd")

boat_passengers_1st_men <- boat_passengers %>% 
  filter(class == "1st",
         gender == "male")

boat_passengers_1st_women <- boat_passengers %>% 
  filter(class == "1st",
         gender == "female")

boat_passengers_2nd_men <- boat_passengers %>% 
  filter(class == "2nd",
         gender == "male")

boat_passengers_2nd_women <- boat_passengers %>% 
  filter(class == "2nd",
         gender == "female")

boat_passengers_3rd_men <- boat_passengers %>% 
  filter(class == "3rd",
         gender == "male")

boat_passengers_3rd_women <- boat_passengers %>% 
  filter(class == "3rd",
         gender == "female")

f_ <- boat_passengers_1st %>% 
  filter(survived == "yes") %>% 
  summarise(prob = round(n() / nrow(boat_passengers_1st), 3))

f_m <- boat_passengers_1st_men %>% 
  filter(survived == "yes") %>% 
  summarise(prob_men = round(n() / nrow(boat_passengers_1st_men), 3))

f_w <- boat_passengers_1st_women %>% 
  filter(survived == "yes") %>% 
  summarise(prob_women = round(n() / nrow(boat_passengers_1st_women), 3))

s_ <- boat_passengers_2nd %>% 
  filter(survived == "yes") %>% 
  summarise(prob = round(n() / nrow(boat_passengers_2nd), 3))

s_m <- boat_passengers_2nd_men %>% 
  filter(survived == "yes") %>% 
  summarise(prob_men = round(n() / nrow(boat_passengers_2nd_men), 3))

s_w <- boat_passengers_2nd_women %>% 
  filter(survived == "yes") %>% 
  summarise(prob_women = round(n() / nrow(boat_passengers_2nd_women), 3))

t_ <- boat_passengers_3rd %>% 
  filter(survived == "yes") %>% 
  summarise(prob = round(n() / nrow(boat_passengers_3rd), 3))

t_m <- boat_passengers_3rd_men %>% 
  filter(survived == "yes") %>% 
  summarise(prob_men = round(n() / nrow(boat_passengers_3rd_men), 3))

t_w <- boat_passengers_3rd_women %>% 
  filter(survived == "yes") %>% 
  summarise(prob_women = round(n() / nrow(boat_passengers_3rd_women), 3))

m_ <- boat_passengers_men %>% 
  filter(survived == "yes") %>% 
  summarise(prob_men = round(n() / nrow(boat_passengers_men), 3))

w_ <- boat_passengers_women %>% 
  filter(survived == "yes") %>% 
  summarise(prob_women = round(n() / nrow(boat_passengers_women), 3))

first_class <- cbind(f_, f_m, f_w)
second_class <- cbind(s_, s_m, s_w)
third_class <- cbind(t_, t_m, t_w)

all_classes <- rbind(first_class,
                     second_class,
                     third_class)

all_classes
```

# Consolidation

## Question 1.
If I roll a six-sided dice once, what is the probability of getting a number less than 5?

```{r}
s_die <- rolldie(1)

s_die %>% 
  filter(X1 < 5) %>% 
  summarise(prob = n() / nrow(s_die))
```

2 / 3

## Question 4.
Five chairs are placed in a row in a room, along with five people of differing height. The people sit down randomly on the chairs. What is the probability that they sit in order of decreasing height, left to right?

```{r}
people <- c("Height1", "Height2", "Height3", "Height4", "Height5")
```

```{r}
chairs <- as_tibble(permutations(n = 5, 
                                 r = 5, 
                                 v = people, 
                                 repeats.allowed = FALSE))

nrow(chairs)
```

1 / 120

## Question 5.
I roll six dice:

what is the probability I see the numbers 6, 5, 4, 3, 2 and 1 in order on the dice, left to right?
what is the probability I see one each of the numbers 6, 5, 4, 3, 2 and 1 on the dice regardless of order?

```{r}
s_die_six <- as_tibble(permutations(n = 6,
                                    r = 6,
                                    v = 1:6,
                                    repeats.allowed = TRUE))

s_die_six_unordered <- as_tibble(permutations(n = 6,
                                              r = 6,
                                              v = 1:6,
                                              repeats.allowed = FALSE))

nrow(s_die_six)

nrow(s_die_six_unordered) / nrow(s_die_six)
```
1 / 46,656 of 6:1

720 / 46,656 of any permutation of 1:6. Around about 1.54%

## Question 6.
If I draw a single card from a 52-card deck, and it is black, what is the probability that its suit is spades?

```{r}
deck <- cards(jokers = FALSE)

deck_black <- deck %>% 
  filter(suit %in% c("Club", "Spade"))

deck_spade <- deck %>% 
  filter(suit == "Spade")

nrow(deck_spade) / nrow(deck_black)
```

50:50