---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(infer)
library(fastGraph)

houses <- read_csv("data/ames.csv") %>% 
  clean_names()
```

# Task 2

>Investigate the distribution of lot_area. Is the distribution roughly normal? If not, what problems do you find?

```{r}
houses %>% 
  ggplot(aes(x = lot_area)) +
  geom_histogram()

houses %>% 
  summarise(min = min(lot_area),
            max = max(lot_area))

houses %>% 
  filter(lot_area < 30000) %>% 
  ggplot(aes(x = lot_area)) +
  geom_histogram() +
  labs(title = "< 30,000")

houses %>% 
  filter(lot_area > 30000) %>% 
  ggplot(aes(x = lot_area)) +
  geom_histogram() +
  labs(title = "> 30,000")
```

> Most of the lots are clustered under 30,000, but there is some extreme outliers, maxing out at 215,245

# Task 3

```{r}
area_bootstrap <- houses %>% 
  specify(response = lot_area) %>% 
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "mean")

area_bootstrap %>% 
  ggplot(aes(x = stat)) +
  geom_histogram(colour = "white")
```

# Task 4

```{r}
area_95_ci <- area_bootstrap %>% 
  get_ci(level = 0.95, type = "percentile")

area_bootstrap %>% 
  ggplot(aes(x = stat)) +
  geom_histogram(col = "white") +
  geom_segment(x = area_95_ci$lower_ci, xend = area_95_ci$upper_ci,
               y = 0, yend = 0, colour = "red", size = 2, lineend = "square") +
  geom_vline(x = mean(houses$lot_area), xintercept = mean(houses$lot_area),
             colour = "red") 
```

# Task 5
>You would like to know the mean(lot_area) of the sold houses with higher confidence. Calculate the 99% CI for this variable. Is it narrower or broader than the 95% CI? Does that make sense?

```{r}
area_99_ci <- area_bootstrap %>% 
  get_ci(level = 0.99, type = "percentile")

area_bootstrap %>% 
  ggplot(aes(x = stat)) +
  geom_histogram(col = "white") +
  geom_segment(x = area_99_ci$lower_ci, xend = area_99_ci$upper_ci,
               y = 0, yend = 0, colour = "blue", size = 2, lineend = "square") +
  geom_segment(x = area_95_ci$lower_ci, xend = area_95_ci$upper_ci,
               y = 0, yend = 0, colour = "red", size = 2, lineend = "square") +
  geom_vline(xintercept = mean(houses$lot_area),
             colour = "red") 

area_bootstrap %>% 
  visualise(bins = 30) +
  shade_ci(endpoints = area_95_ci,fill = "red",  color = "red") +
  shade_ci(endpoints = area_99_ci)
```

>The CI is broader at 99% CI. This makes sense, as to be more confident with the same data, you need to allow more values to be possible.

# Task 6
> Calculate the point estimate of the mean(lot_area)

```{r}
tibble(bootstrap_area_mean = mean(area_bootstrap$stat),
       sample_area_mean = mean(houses$lot_area))
```

# Extension

>Calculate a point estimate and 95% CI for the proportion of houses in the data built before 1920. Does the number of reps you use matter? [Investigate reps from 200 up to 50000, memory of your laptop permitting].

```{r}
bootstraps <- c(200, 1000, 5000, 25000, 50000)
results <- tibble()
for(i in 1:5){
  
  pre_1920_bootstrap <- houses %>% 
  group_by(year_built) %>%  
  mutate(pre_1920 = if_else(year_built < 1920, "Yes", "No")) %>% 
  ungroup() %>% 
  specify(response = pre_1920, success = "Yes") %>% 
  generate(reps = bootstraps[i], type = "bootstrap") %>% 
  calculate(stat = "prop")
  
  pre_1920_95_ci <- pre_1920_bootstrap %>% 
  get_ci(level = 0.95, type = "percentile") %>% 
    mutate(reps = bootstraps[i],
           mean = mean(pre_1920_bootstrap$stat))
  
  results <- results %>% 
    bind_rows(pre_1920_95_ci)
}

results %>% 
  select(3:4,1:2)
```

> The mean proportion gets very slightly smaller as you perform more reps, but it's extremely negligible


